---
title: "Differential Expression Analysis with EdgeR"
output: html_document
---

source("http://www.Bioconductor.org/biocLite.R")
biocLite("BiocUpgrade")
biocLite( "ShortRead")
,	"edgeR")	)
library(edgeR)
library(ShortRead)

#get report
```{r}
setwd("~/Downloads/Gertz_assignment/fastqs/")
fqQC = qa(dirPath=".", pattern=".fastq$", type="fastq")
report(fqQC, type="html", dest="fastqQAreport")
class(fqQC)
```

1) Inspect   the	html	output and	determine	what’s	wrong	with	 test1.fastq?		What	would	you	
do	about	this	issue?


```{r}

```

2) Name   an	 alignment	 program	 that	 you	 would	 use	 to	 align	 RNA-seq	 reads?	 	Why	 is	 that	
aligner	an	appropriate	choice	for	RNA-seq	data?	

3 ) Once  you	have	alignments	to	the	genome,	the	next	step	is	to	determine	how	many	reads	
map	 to	 each	 gene	 or	 transcript.	 	 Assuming	 you	 have	 an	 aligned	 sam	 file	 named	
aligned.sam,	 a	 gtf	 file	 named	 genes.gtf,	 and	 want	 to	 generate	 a	 counts	 file	 named	
genes.cout,	write	 out	 the	 Unix	 command	 you	 would	 run	 to	 generate	 counts	 using	
HTSeq.		You	can	refer	to	page	1776	of	Anders	et	al.

```{r}

```

4) After  step	14A.vi,	inspect	the	relationship	of	the	samples.		Are	any	of	the	samples	outliers?		
What	could	explain	the	presence	of	an	outlier sample?

5) After	step	14B.vi,	look	at	tt$table	and	figure	out	the	percent	knockdown	that	was	achieved	
for	pasilla	(FBgn0261552).		(Hint: logFC	is	log	base	2	of	the	fold	change	in	expression)

6) How	 many	 genes	 are expressed	 differentially	 due	 to	 pasilla	 knockdown	 at a	 False	
Discovery	Rate	(FDR)	of 5%?		(Hint:	The	first	command	in	step	14B.viii	is	a	good	start)
